---
title: "Introduction to this package"
author: "Jie Ding and Xiaoguang Wang"
date: "2021/7/25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



The main function in the package is geecure and its synopsis is: 
 : \code{AR.AuxSP.AGMM( formula, data, aux, na.action = na.omit, lambdas = NULL, lambdas.num = 10, trace.cv = FALSE )

We briefly explain some of the important options. 
The first argument formula specifies the model. It uses the same syntax as the formula argument in survreg in the R package survival. A typical specification involves an object
created by Surv based on survival times and censoring indicators, followed by \code{~} and then names of variables in X concatenated with + or *.


## Implentation

Library the package
```{r library, eval=TRUE}
library(survival)
library(Matrix)
library(survaux)
```

prepare the auxiliary information
```{r preparation, eval=TRUE}
data("toydata1")
gXcut <- function(X){  # group function
rbind(  ( X[,1] >= 0.5 & X[,2] == 0),
        ( X[,1] <  0.5 & X[,2] == 0),
        ( X[,1] >= 0.5 & X[,2] == 1),
        ( X[,1] <  0.5 & X[,2] == 1)
) * 1
}
phi.true <- c(0.646,0.732,0.433,0.491)
tau <- c(0.2,0,0,0)
phi <- phi.true - tau
aux <- list(tstar=0.5,phi=phi,
            G=gXcut(toydata1[,c("X1","X2")]))
```


fit the AGMM model
```{r AR.AuxSP.AGMM, eval=TRUE, results='hold'}
AGMMfit <- AR.AuxSP.AGMM(Surv(yobs,delta)~X1+X2,data=toydata1,aux=aux)
```


From the results, we find that


We can also plot the cv curve







